Multi-modality Imagery Database for Plant Phenotyping

### 2015-07-30 datapaper_hardware.tex
add comments from Jeff

\subsubsection{Fluorescence and IR Images}
Chlorophyll {\it a} fluorescence images were captured once every hour during the daylight period in a growth chamber~\cite{cruz2015depi}.
A set of $5$ images were captured using a Hitachi KP-F$145$GV CCD camera (Hitachi Kokusai Electric America Inc., Woodbury, NY) outfitted with an infrared long pass filter (Schott Glass RG-$9$, Thorlabs, Newton, NJ), during a short period ($<400~ms$) of intense light saturating to photosynthesis ($>10,000~\mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, $5700$K color temperature, Digi-Key, Thief River Falls, MN) collimated using a $20~mm$ Carclo Lens ($10003$, LED Supply, Lakewood, CO).
Chlorophyll {\it a} fluorescence was excited using monochromatic red LEDs (Everlight $625~nm$, ELSH-F51R1-0LPNM-AR5R6, Digi-Key), collimated (which means to make the light rays parallel) using a Ledil reflector optic ($C11347\_REGINA$, Mouser Electronics, Mansfield, TX) and pulsed for $50~\mu s$ during a brief window when the white LEDs were electronically shuttered.
In addition, a series of $5$ images were also collected in the absence of the excitation light for artifact subtraction.

Infrared images were collected once every hour with the same camera and filter used for chlorophyll {\it a} fluorescence.
Pulses of $940~nm$ light were provided by an array of OSRAM LEDs (SFH $4239$, Digi-Key), collimated using a Polymer Optics lens (Part no. $170$, Polymer Optics Ltd., Berkshire, England).
Since $940~nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period~\cite{eskins1992light}.
Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800~nm$) in the region where we do IR reflectance ($940~nm$)~\cite{butler1964actton}.
Note that the other modalities were captured only at day time, so that they will not interfere plant growth.

>>>>

\subsubsection{Fluorescence and IR Images}
Chlorophyll {\it a} fluorescence images were captured once every hour during the daylight period in a growth chamber~\cite{kramer2015plant}.
A set of $5$ images were captured using a Hitachi KP-F$145$GV CCD camera (Hitachi Kokusai Electric America Inc., Woodbury, NY) outfitted with an infrared long pass filter (Schott Glass RG-$9$, Thorlabs, Newton, NJ), during a short period ($<400~ms$) of intense light saturating to photosynthesis ($>10,000~\mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, $5700$K color temperature, Digi-Key, Thief River Falls, MN) collimated using a $20~mm$ Carclo Lens ($10003$, LED Supply, Lakewood, CO).
Chlorophyll {\it a} fluorescence was excited using monochromatic red LEDs (Everlight $625~nm$, ELSH-F51R1-0LPNM-AR5R6, Digi-Key), collimated (minimizing the dispersion of light) using a Ledil reflector optic ($C11347\_REGINA$, Mouser Electronics, Mansfield, TX) and pulsed for $50~\mu s$ during a brief window when the white LEDs were electronically shuttered.
In addition, a series of $5$ images were also collected in the absence of the excitation light for artifact subtraction.

Infrared images were collected once every hour with the same camera and filter used for chlorophyll {\it a} fluorescence.
Pulses of $940~nm$ light were provided by an array of OSRAM LEDs (SFH $4239$, Digi-Key), collimated using a Polymer Optics lens (Part no. $170$, Polymer Optics Ltd., Berkshire, England).
Since $940~nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period~\cite{eskins1992light}.
%Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800~nm$) in the region where we do IR reflectance ($940~nm$)~\cite{butler1964actton}.
Note that the other modalities were captured only at day time, so that they will not interfere with the circadian cycle of the plant.

### 2015-07-30 datapaper_intro.tex
add comments from Jeff

Plants develop through a complex interaction between genotype and environment.
This determines their structure, functions, and thus performance such as yield or efficient usage of resources.
In order to understand the genetic basis of these economically important parameters, it is essential to quantitatively assess plant phenotypes and then identify the latent relationships to genotypes and environmental factors.
%
Plant visual phenotyping has been performed by farmers and breeders for more than $5,000$ years.
In the past, traditional phenotyping is based on experience and intuition, and is laborious~\cite{johannsenerblichkeit}.
Recent progresses in imaging sensor and computer vision technologies lead to the development of the ever-increasing new field of highly automated, non-destructive plant visual phenotyping~\cite{furbank2011phenomics,cruz2015depi}.
%Modern plant phenotyping is a comprehensive, large-scale assessment of plant traits such as growth, development, tolerance, resistance, architecture, physiology, ecology, yield, and metadata that form the basis for more complex parameters.
%
The objective of modern plant visual phenotyping is to analyze and categorize the morphological characteristics of plants, and thus accurately quantifying plant traits. %It advances crop yield improvement and enables the systematic study of the environmental plasticity of plants. %
In this interdisciplinary field, scientists employ various imaging sensors to capture plants and design advanced algorithms to automatically analyze the captured plant imagery, with the purpose of raising testable biological hypotheses to solve problems related to growth, development, stress tolerance, resistance, and so on.
%
%In old days, plant phenotyping was conducted through manual visual observation~\cite{Erblichkeit1903}. Today, motivated by the increasing lower cost and increasing diversity of imaging sensors technologies, image-based automatic plant visual phenotyping is quickly growing into a desirable and viable solution~\cite{furbank2011phenomics,cruz2015depi}.
%
A key advance in visual phenotyping is the capability to non-invasively capture plant traits, enabling continuous measurements that are necessary to monitor plants during growth and/or under stress conditions.
It also increases the throughput of phenotyping experiments by eliminating destructive operations, which allows more genotypes or biological replicates to be examined under the same environmental conditions~\cite{fahlgren2015lights,walter2015plant}.

One goal of plant visual phenotyping is to accurately quantify plant traits, particularly those related to photosynthetic performance, growth, yield, and resilience to environmental stress.
For the approaches to be of practical, plants must be monitored continuously, over developmental time scales and under conditions that approximate the native environment (dynamic 'field' conditions)~\cite{fahlgren2015lights,walter2015plant}.
%
The capacity to identify and track individual leaves over time is important to clearly define phenotypic behaviors related to leaf-specific factors such as developmental age~\cite{schottler2015photosynthetic} and/or following the application of stress.
For example, decrease in the average photosynthetic efficiency ($\Phi_{II}$, quantum yield of photochemistry at photosystem II) of an Arabidopsis plant may reflect a heterogeneous distribution of $\Phi_{II}$ values across its entire photosynthetic surface area~\cite{oxborough2004imaging}.
In this case, mapping distributions to individual leaves can distinguish between a systemic (whole plant) effect and localization of the effect to subset leaves.
%
In addition, using more detailed information, such as leaf angles, height, and position as well as canopy density and size, it is possible to improve the estimation of total photosynthetic capacity over time (particularly for plants with more complex canopies, e.g., common bean or tobacco), since these factors influence absorption and availability of the light energy used to drive photosynthesis.

>>>>

% Jeff corrected
The complex interaction between genotype and environment determines how plants will develop physiologically (from the biochemical level to structural morphology), which ultimately influences field performance, for example resource acquisition, resource partitioning and seed yield.  
In order to understand the genetic basis for these economically important parameters, it is essential to quantitatively assess plant phenotypes and then identify the latent relationships between genotype and environmental factors.  
Plant visual phenotyping has been performed by farmers and breeders for more than $5,000$ years to develop plant lines with desirable traits.  
This traditional method is based on experience and intuition and is both labor intense and time-consuming~\cite{johannsenerblichkeit}.  
Recent progress in imaging sensor, robotics and automation technologies has recently led to the rapid development of highly-automated, non-destructive, high-throughput methods for visual phenotyping ~\cite{furbank2011phenomics,kramer2015plant}.  
The intent of modern plant visual phenotyping is to accelerate the collection, analysis and categorization visual (e.g. morphology, size) and spectral (e.g. chlorophyll fluorescence, chlorophyll content, water content, leaf temperature) data sets in order to identify and quantify specific plant traits, especially those related to plant performance. 
This interdisciplinary field requires scientists and engineers to not only develop or employ various image sensors platforms to collect under relevant conditions, but also design advance algorithms for the automated processing and analysis of image data.

%Plants develop through a complex interaction between genotype and environment.
%This determines their structure, functions, and thus performance such as yield or efficient usage of resources.
%In order to understand the genetic basis of these economically important parameters, it is essential to quantitatively assess plant phenotypes and then identify the latent relationships to genotypes and environmental factors.
%Plant visual phenotyping has been performed by farmers and breeders for more than $5,000$ years.
%In the past, traditional phenotyping is based on experience and intuition, and is laborious~\cite{johannsenerblichkeit}.
%Recent progresses in imaging sensor and computer vision technologies lead to the development of the ever-increasing new field of highly automated, non-destructive plant visual phenotyping~\cite{furbank2011phenomics,cruz2015depi}.
%The objective of modern plant visual phenotyping is to analyze and categorize the morphological characteristics of plants, and thus accurately quantifying plant traits. %It advances crop yield improvement and enables the systematic study of the environmental plasticity of plants. %
%In this interdisciplinary field, scientists employ various imaging sensors to capture plants and design advanced algorithms to automatically analyze the captured plant imagery, with the purpose of raising testable biological hypotheses to solve problems related to growth, development, stress tolerance, resistance, and so on.
%A key advance in visual phenotyping is the capability to non-invasively capture plant traits, enabling continuous measurements that are necessary to monitor plants during growth and/or under stress conditions.
%It also increases the throughput of phenotyping experiments by eliminating destructive operations, which allows more genotypes or biological replicates to be examined under the same environmental conditions~\cite{fahlgren2015lights,walter2015plant}.

One goal of plant visual phenotyping is to accurately determine genetic components related to photosynthetic performance, growth, yield, and resilience to environmental stress.
For this approach to be of effective, plants must be monitored continuously, over developmental time scales and under conditions that approximate the native environment (dynamic 'field' conditions)~\cite{fahlgren2015lights,walter2015plant}.
The capacity to identify and track individual leaves over time is important to clearly define phenotypic behaviors related to leaf-specific factors such as developmental age~\cite{schottler2015photosynthetic} and/or following the application of stress.
For example, decrease in the average photosynthetic efficiency ($\Phi_{II}$, quantum yield of photochemistry at photosystem II) of an Arabidopsis plant may reflect a heterogeneous distribution of $\Phi_{II}$ values across its entire photosynthetic surface area~\cite{oxborough2004imaging}.
In this case, mapping distributions to individual leaves can distinguish between a systemic (whole plant) effect and localization of the effect to subset leaves.
In addition, using more detailed information, such as leaf angles, height, and position as well as canopy density and size, it is possible to improve the estimation of total photosynthetic capacity over time (particularly for plants with more complex canopies, e.g., common bean or tobacco), since these factors influence absorption and availability of the light energy used to drive photosynthesis.

### 2015-07-30 datapaper_prior.tex
add comments from Jeff

The four sensing modalities in MSU-PID provide unique opportunities to comprehensively characterize plant morphological and physiological phenotypes.
The use of chlorophyll fluorescence at $730$ $nm$ to $750$ $nm$ as a tool for evaluating photosynthetic performance is well established~\cite{baker2008chlorophyll}, and against non-(chlorophyll)fluorescent background clearly defines photosynthetically active leaf area.
The depth measurement has been a component of a number of recent non-plant RGB-D databases designed for object recognition~\cite{Lai2011}, scene segmentation~\cite{Silberman2011}, human analysis~\cite{Sung2011,Barbosa:reid12}, and mapping~\cite{sturm12iros}.
By including depth map for a plant database, we anticipate enabling development of new $3$D plant canopy analysis algorithms and thus probing the total energy intake and storage.
Near infrared (IR) reflectance has been used by others to detect water content in leaves~\cite{chen2014dissecting}.
However, it may also be useful in determining leaf angle and curvature.
Furthermore, since imaging occurs at a wavelength that is effectively non-absorbing for photosynthesis or known light receptors~\cite{butler1964actton,eskins1992light} in plants, it can be used for imaging during the night cycle to observe night time leaf expansion or in some cases circadian movements~\cite{mcclung2006plant}.

>>>>

The four sensing modalities in MSU-PID provide unique opportunities to comprehensively characterize plant morphological and physiological phenotypes.
The use of chlorophyll fluorescence at $730$ $nm$ to $750$ $nm$ as a tool for evaluating photosynthetic performance is well established~\cite{baker2008chlorophyll}, and against non-fluorescent background, it clearly defines the chlorophyll-containing (photosynthetically active) leaf area.
The depth measurement has been a component of a number of recent non-plant RGB-D databases designed for object recognition~\cite{Lai2011}, scene segmentation~\cite{Silberman2011}, human analysis~\cite{Sung2011,Barbosa:reid12}, and mapping~\cite{sturm12iros}.
By including depth map for a plant database, we anticipate enabling development of new $3$D plant canopy analysis algorithms and thus probing the total energy intake and storage.
Near infrared (IR) reflectance at $\sim940~nm$ has been used by others to detect water content in leaves~\cite{chen2014dissecting}.
However, it may also be useful in determining leaf angle and curvature~\cite{woolley1971reflectance}.
Furthermore, since imaging occurs at a wavelength that is effectively non-absorbing for photosynthesis or known light receptors~\cite{butler1964actton,eskins1992light} in plants, it can be used for imaging during the night cycle to observe night time leaf expansion or in some cases circadian movements~\cite{mcclung2006plant}.

### 2015-07-30 datapapr_labeling.tex
add comments from Jeff

It is often argued which is the best setting due to the trade-off between the image resolution and the throughput of phenotyping experiments.
We chose to image a whole tray of Arabidopsis at lower resolution rather than an individual at higher resolution, because it better reflects high-throughput protocols, which in practice allows direct comparison of multiple genotypes in the same experiment.
In contrary, we chose to image a single bean plant because we anticipate enabling development of $3$D plant canopy reconstruction algorithms for bush plants.

@@

For Arabidopsis images, we label $4$ frames each day.
While for bean images, we label $7$ frames each day because of their spontaneous and fast leaf movement.
A Matlab GUI interface is developed for leaf labeling, as shown in Figure~\ref{fig:label}, which will also be available to the public.
A user can open a plant image (``Open") to label the two tips and annotate each leaf segment.
The results will be automatically saved once a user moves to a previous or next image (``Previous", and ``Next").
For consistent annotation of the same leaf over time, we show a number on the center of each leaf indicating the order of labeling from the previous frame.

The labeling of the leaf segment (``Leaf Label") is implemented by clicking the boundary of one leaf at each time.
In order to provide more accuracy labeling, we click very dense points ($\sim20$ points on average for each leaf) on the boundary.
The labeled leaf boundary is overlaid on the image for better visualization to guide the next action.
Incorrect label can be deleted right after the labeling by clicking ``Clear".
All leaf labels can be deleted by clicking ``Clear All".
This process continues until all leaf segments have been annotated.
Once a leaf is invisible due to occlusion, the label can be skipped by clicking ``Invisible".

@@

We can make two conclusions from Table~\ref{tab:labelError}.
First, the similarity for both manual annotation and label propagation increases as the plant grows.
This is expected because {\it{SBD}} depends on the overlap ratio between two leaves, which inherently favors larger leaves.
Second, the performance of label propagation is only slightly worse than the performance of human annotations.
Therefore, we use label propagation to provide the labels for all four modalities for Arabidopsis sequences, which not only saves laborious human labor, but also provides consistent labels for all four modalities.

>>>>

%It is often argued which is the best setting due to the trade-off between the image resolution and the throughput of phenotyping experiments.
The trade-off between image resolution and sample throughput is a common conundrum with designing visual phenotyping experiments. 
We chose to image a whole tray of Arabidopsis at lower resolution rather than an individual at higher resolution, because it better reflects high-throughput protocols, which in practice allow direct comparison of multiple genotypes in the same experiment.
In contrast, we chose to image a single bean plant because we anticipate enabling development of $3$D plant canopy reconstruction algorithms for bushy plants.

@@

For Arabidopsis images, we labeled $4$ frames per day.
While for bean images, we labeled $7$ frames per day due to the plant's fast and spontaneous leaf movements. 
A Matlab GUI interface was developed for leaf labeling, as shown in Figure~\ref{fig:label}, which will be available to the public.
A user can open a plant image (``Open") to label the two tips and annotate each leaf segment.
The results will be automatically saved once a user moves to a previous or next image (``Previous", and ``Next").
For consistent annotation of the same leaf over time, we show a number on the center of each leaf indicating the order of labeling from the previous frame.

The labeling of the leaf segment (``Leaf Label") is implemented by clicking the boundary of one leaf at each time.
In order to provide more accurate labeling, a fairly high point density ($\sim20$ points on average) is typically used to define the boundary for each leaf. .
The labeled leaf boundary is overlaid on the image for better visualization to guide the next action.
An incorrect label can be deleted right after the labeling by clicking ``Clear", or all leaf labels can be deleted by clicking ``Clear All".
This process continues until all leaf segments have been annotated.
Once a leaf is invisible due to occlusion, the label can be skipped by clicking ``Invisible".

@@

We can make two conclusions from Table~\ref{tab:labelError}.
First, the similarity for both manual annotation and label propagation increases as the plant grows.
This is expected because {\it{SBD}} depends on the overlap ratio between two leaves, which inherently favors larger leaves.
Second, the performance of label propagation is only slightly worse than the performance of human annotations.
Therefore, we use label propagation to provide the labels for all four modalities for Arabidopsis sequences.
There are two benefits: $1)$ it decreases the need for manual label; $2)$ labeling is consistent for all four modalities. 
%, which not only saves laborious human labor, but also provides consistent labels for all four modalities.
